$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-01 paper/paper.tex
Add some references to related work

@@

    \item
      For constructor $\constr{recv}$ we split $\Delta$ so that we can proceed inductively on the continuation.
      We first observe that given that there exists an arrow from $\Gamma_i$ to $\Psi_i$ and $\Delta$ at index $i$ is $\lz$, for any $m$ and $n$, there is some $\delta$ such that $\opsquared{m}{\delta}{n}$.
 l     \begin{itemize}
        \item
          If the input occurs on the variable that is being substituted, we derive $\opsquared{m}{\li}{l}$ for some $l$ and construct an arrow $\containsusage{\Xi_i}{i}{l}{\Gamma}$ (used for the inductive call).
          Similarly, we construct the arrows $\containsusage{\Gamma_j}{j}{\li}{\Xi_j}$ (used as the new channel on which input occurs) and $\containsusage{\Xi_j}{j}{l}{\Gamma}$ (used for the inductive call) for some $\Xi_j$.
        \item
          If the input occurs on some variable $x$ other than the one that is being substituted, we construct the arrows $\containsusage{\Xi_i}{i}{m}{\Theta}$ (used for the inductive call) and $containsusage{\Gamma}{x}{\li}{\Theta}$ for some $\Theta$.
          We can then find $\Xi_j$ and construct the two arrows $\containsusage{\Gamma_j}{x}{\li}{\Xi_j}$ (used as the new channel on which input occurs) and $\containsusage{Xi_j}{j}{m}{\Theta}$ (used for the inductive call).
          From the fact that there exists a composition of arrows from $\Xi_i$ to $\Psi$, we can conclude that $\Theta$ is splitting $\Delta$ such that $\opctx{\Gamma}{\Delta_1}{\Theta}$ and $\opctx{\Theta}{\Delta_2}{\Psi}$.
          As $\lz$ is a minimal element, if $\Delta$ is $\lz$ at index $i$, then it must be $\lz$ at index $i$ for $\Delta_1$ and $\Delta_2$ as well.
      \end{itemize}

@@

@@

\cite{typing-with-leftovers}

\cite{Higher-inductive-types-for-congruence}

@@

\cite{work-on-session-types}

>>>>

\todo{highlight that we can talk about a resource even if it has been exhausted (e.g. we can send 0 multiplicities of a channel over another channel}

@@

    \item
      For constructor $\constr{recv}$ we split $\Delta$ so that we can proceed inductively on the continuation.
      We first observe that given that there exists an arrow from $\Gamma_i$ to $\Psi_i$ and $\Delta$ at index $i$ is $\lz$, for any $m$ and $n$, there is some $\delta$ such that $\opsquared{m}{\delta}{n}$.
 l     \begin{itemize}
        \item
          If the input occurs on the variable that is being substituted, we derive $\opsquared{m}{\li}{l}$ for some $l$ and construct an arrow $\containsusage{\Xi_i}{i}{l}{\Gamma}$ (used for the inductive call).
          Similarly, we construct the arrows $\containsusage{\Gamma_j}{j}{\li}{\Xi_j}$ (used as the new channel on which input occurs) and $\containsusage{\Xi_j}{j}{l}{\Gamma}$ (used for the inductive call) for some $\Xi_j$.
        \item
          If the input occurs on some variable $x$ other than the one that is being substituted, we construct the arrows $\containsusage{\Xi_i}{i}{m}{\Theta}$ (used for the inductive call) and $\containsusage{\Gamma}{x}{\li}{\Theta}$ for some $\Theta$.
          We can then find $\Xi_j$ and construct the two arrows $\containsusage{\Gamma_j}{x}{\li}{\Xi_j}$ (used as the new channel on which input occurs) and $\containsusage{Xi_j}{j}{m}{\Theta}$ (used for the inductive call).
          From the fact that there exists a composition of arrows from $\Xi_i$ to $\Psi$, we can conclude that $\Theta$ is splitting $\Delta$ such that $\opctx{\Gamma}{\Delta_1}{\Theta}$ and $\opctx{\Theta}{\Delta_2}{\Psi}$.
          As $\lz$ is a minimal element, if $\Delta$ is $\lz$ at index $i$, then it must be $\lz$ at index $i$ for $\Delta_1$ and $\Delta_2$ as well.
      \end{itemize}

@@

\cite{Allais2018a}
typing with leftovers
bidirectional typing rules
decidable typechecking and type inference
limited to a linear type system
framing, weakening, substitution
soundness and completeness with respect to a sequent calculus for intuitionistic linear logic

\cite{Thiemann2019}
\cite{Rouvoet2020}
\cite{Veltri2020}

@@

@@
